Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-14 manuscript.tex
Consistency [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/1d039da4feb8d403df76f2947e56c04eb948cf71.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/1d039da4feb8d403df76f2947e56c04eb948cf71/checks
https://github.com/habi/acinar-analysis-manuscript/runs/420935071

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681} and is under revision in the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...a04b78817dad0c1dd6ce05f2e961363c2da567ba}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/a04b78817dad0c1dd6ce05f2e961363c2da567ba/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/a04b78817dad0c1dd6ce05f2e961363c2da567ba}{habi/acinar-analysis-manuscript@a04b788}
on December 11, 2020.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a04b788)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a04b788)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}

@@

Based on the acinar and parenchymal volume we calculated the number of acini and were able to verify the previously reported results to lie within our margin of error at days 4 and 60 (Barré et al: 6236~±~497~acini and 5612~±~547~acini, respectively).
As shown in figure~\ref{fig:07}, our values \(\pm\) their standard deviation are overlapping the previously found values, even though we generally see a trend that the number of acini seems to decrease during lung development.
This might be due to fusing of several acini to one or simply because we missed some acini in the analysis of the large datasets.

@@

\leavevmode\hypertarget{ref-199ALtdJt}{}%
53. Replacement, Reduction, Refinement {[}Online{]}. \emph{ALTEX} 19: 73--78, 2002. \url{https://www.altex.org/index.php/altex/article/view/1106} {[}11 Dec. 2020{]}.
\end{cslreferences}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681} and is under revision in the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...1d039da4feb8d403df76f2947e56c04eb948cf71}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/1d039da4feb8d403df76f2947e56c04eb948cf71/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/1d039da4feb8d403df76f2947e56c04eb948cf71}{habi/acinar-analysis-manuscript@1d039da}
on December 14, 2020.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(1d039da)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(1d039da)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Switzerland
\end{itemize}

@@

Based on the acinar and parenchymal volume we calculated the number of acini and were able to verify the previously reported results to lie within our margin of error at days 4 and 60 (Barré et al: 6236~±~497~acini and 5612~±~547~acini, respectively).
As shown in figure~\ref{fig:07}, our values ± their standard deviation are overlapping the previously found values, even though we generally see a trend that the number of acini seems to decrease during lung development.
This might be due to fusing of several acini to one or simply because we missed some acini in the analysis of the large datasets.

@@

\leavevmode\hypertarget{ref-199ALtdJt}{}%
53. Replacement, Reduction, Refinement {[}Online{]}. \emph{ALTEX} 19: 73--78, 2002. \url{https://www.altex.org/index.php/altex/article/view/1106} {[}14 Dec. 2020{]}.
\end{cslreferences}
